\section*{Article IV: Officers}
\addcontentsline{toc}{section}{Article IV: Officers}

\begin{enumerate}
    \item The officers of this Chapter shall be: Chair, Vice Chair, and Treasurer.
    These individuals must be ACM Student Members.
    In addition, a Faculty Sponsor with an ACM Professional Membership is required.
    These officers constitute the Council.
    A minimum of three officers to establish a Chapter. Other officers may also be established.
    \item All required officers of the Chapter must be members of ACM.
    The officers shall be elected by a plurality of the votes cast at the annual election meeting.
    They shall take office on January 1 and serve for one year.
    \footnote{
      It is highly recommended that the Chapter's election be held at the last meeting in the fall with the new officers taking office in January.
    This provides for a period of transition from the outgoing Council to the incoming Council as well as providing continuity of management and planning over the summer.
    If your school operates on a quarter or trimester system, choose a timing that serves the same objectives.}
  \item Appointment or nomination of an individual to an officer positions within ACM shall be in general limited to two full consecutive terms in the same position.
  This recommendation is intended to encourage the continuing infusion of new volunteers into the organization and to encourage office holders to give thought to planning for their successor.
  Appointment or nomination to a third or subsequent consecutive term should be limited to situations where such appointment or nomination is believed to be in the best interests of the Association.
\end{enumerate}
