\section*{Article VI: Chapter Sponsor}
\addcontentsline{toc}{section}{Article VI: Chapter Sponsor}

The Sponsor shall be a faculty member or full-time staff member of your school. Each Student Chapter has one Sponsor.

\begin{enumerate}
    \item The Student Chapter Sponsor shall be a voting member of ACM and either a member of the faculty or full-time staff of the Clemson University.
    \item The Student Chapter Sponsor shall be selected by the Executive Council immediately following the Election Meeting. The selection shall be confirmed by the school.
    \item The Student Chapter Sponsor shall be generally responsible for the activities of the Chapter. Specifically, the Sponsor:
    \begin{itemize}
        \item helps provide continuity from year to year as student leadership and personnel change;
        \item promotes good student-faculty relationships;
        \item helps maintain university standards in all activities of the Chapter;
        \item exercises financial supervision, if necessary, by promoting prompt payment of bills and collection of dues, and overseeing the settlement of all accounts in the event of dissolution of the Chapter.
        \item represents the Chapter interests to the faculty and administration.
        \item for high school chapters and underage students, the chapter sponsor must be in attendance at every meeting that is held in the evening.
        In the event that the appointed sponsor is not available, another faculty member may chaperon the meeting.
        If both are not available, a local area professional, previously investigated and approved by the school, can be assigned to supervise evening meetings.
    \end{itemize}
\end{enumerate}
